The related works highlight how important presence is for training simulations.
A combined approach of clincal examination together with 3D inspection of the patient has an unprecedented potential toward the diagnosis of the patient with a maxillofacial deformity \cite{swennen2009three} by providing a virtual inspection of the patient’s anatomy.
This is precisely why this thesis proposes a novel approach to existing methods.
Since commercially available hardware today is able to produce high fidelity visuals and an immersive, stereoscopic view of virtual objects,
the natural conclusion is to try out innovative approaches to existing problems with them.
It also highlights how important a 1:1 real world scale is for visualizing the spatial relationships in patient's anatomy and pathology.
Additionally, not only the surgical environment, but also the interactions, usability and the users representation in the VR have to be considered.
\\ Based on the related work described in Section \ref{sec::RelatedWork} and the goal of the thesis outlined in Section \ref{chap::Introduction}, a requirement analysis has been conducted.
The requirement analysis is divided in non-functional and functional requirements.
Afterwards, based on the functional and non-functional requirements, a concept is then finalized and described.

\section{\label{sec::RequirementAnalysis}Requirement Analysis}
\input{sections/3_approach/requirement_analysis/main.tex}
\section{\label{sec::Concept}Concept}
\input{sections/3_approach/concept/main.tex}