In this section, a number of endevours for surgical simulations in virtual reality will be presented.
This section gives a broad overview of previous VR-based simulations for surgeons in training.
At the end there is discussion about lessons learned from this research.

Parham et. al present a novel approach for a low cost surgical simulation to train novice surgeons for cervical cancer surgery \cite{RN52}.
The simulator aims to create pre-trained novices in resource-challenged countries. 
Cervical cancer is one of the world's leading causes of death \cite{RN52}.

By developing a low cost simulation, using commercially available VR software and the Oculus Rift HMD, they have succesfully 
helped surgeons to prepare for radical abdominal hysterectomy surgery procedures.
A near identical representation of an operating theatre using 1:1 scale was used for immersion.
3D replica of human female pelvic anatomy and pathalogy including organs, veins, peritoneum and connective tissue was created.
A huge focus while developing was to simulate reality as accurately as possible. 
Immersing trainees in the simulator is crucial so that they can focus on learning and practise without distractions.
Putting them in a realistic operating scenario helps reducing anxiety and selfconsciousness before first time operations \cite{RN52}.

Parham et. al recognize a need for clinical testing to establish VR efficacy, since there is a lack of research for VRs clinical utility \cite{RN59}. 
However, VR was already considered over 10 years ago as an important addition to surgical training, with a prediction for even more relevance in the future \cite{RN60}.
These low cost VR applications could be especially considered for resource-challenged countries where there is a lack of skilled workforce, mainly because of cost.

This simulator creates pre-trained novices by providing new ways to acquire the psycho-motor skills, sensory acuity and cognitive planning abilities needed for sugery.
Virtual reality based training is already proven to reduce the time to acquire surgical proficiency \cite{RN61,RN62}. 
In randomized control studies, VR trained trainees performing laparoscopic cholecystectomy, made fewer errors and were faster \cite{RN63,RN64}.
VR trained trainees required only half the time to reach the skill level of intermediately skilled surgeons compared to standard training.
Hence, it is proven that skills acquired in simulations can successfully be translated to the operting theatre (OT) \cite{RN63,RN64}.

Parham et. al focus on high-quality visuals for immersion.
All assets are represented in 1:1 scale and the correct visual reproduction of organs, tools and hand positions is ensured through thorough analysis of real world counterparts.
Object materials are physics-based and organic materials approximated by an physics engine.
The lighting emerging from medical equipment is based on their specifications.
Lastly, the software would be developed with future expansion into other medical fields in mind \cite{RN52}.

The virtual OT consists of the open surgical area including organs of the patient, a tray for surgical instruments and a monitor displaying simulated patient vitals and procedure instructions.
It was modeled after a real world OT located inside the University Teaching Hospital in Lusaka, Zambia.
The assets were modeled after recieving reference photos and videos of locations and instruments and researching the female anatomy.
It was argued that even though 3D scans of real human organs exists, they are too inefficient to run in real time VR \cite{RN52}.

In the virtual reality simulation, the trainee stands in the virtual OT with an operating table, tray of surgical instruments and the surgery awaiting patient with cervical cancer.
The procedure is closely modeled after an actual surgical procedure, meaning the surgical site is exposed while the rest of the patient is covered.
Instructions are given via a monitor above the operating table and audio feedback is given to guide the trainee through the simulation.
The simulation lasts roughly 20 minutes and provides feedback on the trainees accuracy on various postions of the procedure and an overall score.
To compare traditional surgical training versus VR, the trainees are assessed by expert surgeon-mentors \cite{RN52}.

It is mentioned how commercial VR will advance significantly in the future, allowing for an even better adoption of VR simulations in surgery.
Surgical training enhanced with augmented and virtual reality will have wide applications according to Parham et. al.
However, such technology has to be carefully build and clinically tested.
VR and AR has the potential to help train the workforce and to ensure higher quality standards \cite{RN52}.

Another example for virtual reality training tools is the regional anaesthesia simulator (RASim) \cite{RN70}.
RASim focuses on physical accuracy using soft-tissue simulation and a haptic device to improve realism of interactions.
It was developed out of the lack of training opportunities. Even though mannequins exist for training, they are too limited 
as they do not reflect the diversity of different patients and they wear from repeated use \cite{RN70}.

RASim allows for relevant tissue to be viewed.
Tissue is segmented into skin, fat, muscle, blood vessels and bones.
The simulation consists of two steps: First, the user performs a palpation using an extended index finger to sense the right puncture site for the procedure on the patients skin.
Secondly, the user can switch the interaction mode to control a virtual needle.
The needle can be moved freely until the patient's tissue is penetrated.
When penetrating, only the depth of the needle can be varied.
The user can trigger a virtual aspiration at any time to check whether the needle tip penetrated any blood vessel.
If the needle tip is in emission range of any virtual nerve cord, according muscular motor responses are displayed in real-time.
An interesting feature of RASim is the event logger, which remembers any given interaction step and thus allows to replay the whole procedure.
This allows for further assesment by users themselves, but even moreso allows trainees to view the log of an experienced surgeon for learning.

A user study compromised of ten residents and consultants with experience between one and twenty years has been conducted \cite{RN72}.
The overall sentiment towards RASim was positive. Realism of the anatomy and identification of landmarks were highly rated. 
The majority of participants agreed that training with the simulator will be helpful to gain more confidence and increase the rate of successful nerve blocks.
However, the majority of participants stressed that the haptic feedback has to be as sophisticated as possible.

A closely related work is the bilateral sagittal split osteotomy simulator (BSSOSim) \cite{RN69}.
BSSO is a major surgical procedure in maxillofacial surgery where training opportunities are rare and can be harmful for patients.
Similar to RASim, this simulator compromises of realistic haptic feedback and tissue simulation.
The simulator focuses on drilling and breaking, which are a subset of the operation steps in BSSO.

The main goal of the BSSOSim it the training of necessary motor abilities for a successful outcome of the operation.
To achieve the required realism to train motor abilities, a haptic input/output device with 6 degrees of freedom is utilized.
This allows users to get a feel for the exerted force needed in the operation.

NeuroSimVR is another training tool utilizing haptic devices \cite{RN71}.
This simulator allows novice surgeons to learn and practice a spinal pedicle screw insertion (PSI).
Mostafa et. al recognize that most similar simulators perceive limited adoption by some medical experts.
In contrast to related works, NeuroSimVR aims to optimize user interaction and user experience.
The goal is to support medical experts with a training and learning tool that better satisfies their needs and expectations.

Mostafa et. al highlight that users, particularly novices, need an considerable amount of training before they can use and operate many of the existing simulatiors.
Hence, NeuroSimVR has unique educational features and a simplified interface for ease of use.
A key problem with NeuroSimVR as noted by numerous participants of the user study conducted \cite{RN71}, was that the simulation lacked realistic haptic feedback. 
Based on the feedback of their user study, Mostafa et. al concluded a number of key components which should be implemented in future works.

First, a flexible and simplified interaction is very important.
Users especially liked the real-time x-ray visualization of different segmented tissue.
Post simulation performance measures were also highly rated, although irrelevant for this thesis.
Mostafa et. al strongly suggested simplifying the design of interactions when building surgical simulation as an important step towards providing more individualized independent learning.
The ability to adjust the visualization of each anatomy part should be supported.
This includes giving the user the option to hide or show various tissues as well varying their opacity.
All participants of the conducted study stressed that performance measures beyond a simple numerical score provided by the simulation are important.
Integrating feedback in a timely manner can be useful especially whenever something goes wrong.
In NeuroSimVR this was realized by visual blinking if mistakes were made.

The goal of this thesis is to apply virtual reality in oral and maxillofacial surgery treatment planning.
Haptic devices are a challenging aspect of most VR training simulators.
Especially for training motor skills, haptic devices are a necessity.
However, the percieved realism of such devices is still not accurate enough for most applications.
Since the goal of this thesis is not an accurate physical representation of surgery, no haptic devices will be utilized.
In contrast to the presented work, this thesis aims to provide a useful tool not only for learning, but also for planning patient specific surgery.
Because of technology advancing rapidly, VR and AR become more and more affordable options.
Mentioned limitations for patient specific 3D models are not an issue anymore.
By using patient anatomy and pathology specific models, surgeons can profit from the mentioned benefits of VR simulation not only as a learning tool.
Moreover, the goal is to give trained surgeons a useful tool which adds to the arsenal of existing planning techniques.
However, trainees can also benefit immensely by studying and reproducing planned procedures of experts.
Another aspect of VR is the ability to communicate on a global level. 
In fields where expects are rare, planned procedures by such experts could be viewed and studied to get greater insight.
