In this thesis, a pre-operative planning and training tool utilizing
commercially available HMDs, namely HTC Vive and Valve Index Controllers
has been developed. The feasability and usability of 
abstract simulations of procedures in the context of pre-operative planning
and training in OMFS could preliminarily be shown with the 
conducted user study. 
A combination of natural hand gestures, GUI and VUI have been
successfully utilized in such a way that the usability
of the system has been percieved as overwhelmingly positive.
Even though the system was somewhat complex due to the amount of features 
and available tools, users did not feel confused while using the 
system.
The accessability of the developed software, 
as mentioned to be an essential part of developed applications by
Hassfeld et al. \cite{HASSFELD20012}, has been especially considered,
as per requirements depicted in Section \ref{chap::Approach}.
Through the overall concept of the application and the vision of a VR-AR-based workflow, as depicted in Section 
\ref{sec::Concept}, the extensibility of the application should be ensured. 
The efforts made to provide users with an immersive experience,
as depicted in Section \ref{sec::VitualOperatingRoom},
resulted in a high level of presence in the virtual OT felt by the users.
\\ The biggest criticism of the application was the abstract 
simulation of procedures. Unfortunately, haptic feedback devices are still
not commercially available and somewhat expensive input devices. Since
the aim in this thesis was to provide a broadly available, cost-effective
tool, they were not considered here. However, as VR technology progresses,
haptic feedback devices will surely be introduced to the consumer market.
Especially then, they should be utilized in such applications to combat
the major criticism received in the user study.
On the software side, one would also have to make sure that 
the anatomy of the 3D models behaves realistically. This is, as 
presented in the related works, not an easy task. 
Because the focus was an abstraction of procedures by the mere provision 
of instruments, a large number of procedures should be made possible.
In this context, a realisticly behaving surgical procedure is
especially difficult to realize.
In conclusion, it can be said that abstract simulations have a valuable
place as a pre-operative planning and training tool. However, they 
can only complement the pre-existing methods and not replace them.
 
\section{Future Work}
\input{sections/7_conclusion/future_work.tex}





