A key part of this thesis is to advance the area of visualisation of medical imaging.
Even though techniques exist, operations are still planned on two-dimensional images for three-dimensional surgical sites.
\newline
As VR technology advances and entry costs are reduced, VR is considered more and more for a wide spectrum of applications.
In surgery, the main focus of research is on surgical training with pre-modeled patient anatomy and pathology.
By using state-of-the-art medical imaging and virtual reality technology and head mounted displays, this thesis aims to advance medical visualisation and surgery planning for patient specific procedures.
In Section \ref{sec::General}, a number of VR-based surgical simulations in different medical fields will be presented.
In Section \ref{sec::OralAndMaxillofacial}, the OMFS specific training tool "VR Surgery" will be presented.
VR Surgery was developed as a visualisation aid for senior surgeons and as a practice tool for novices.

\subsection{\label{sec::Devices}Used Devices}
\input{sections/2_related_work/subsections/devices.tex}

\subsection{\label{sec::Input}Input Devices and Haptic Feedback}
\input{sections/2_related_work/subsections/input.tex}

\subsection{\label{sec::Visualization}Visualization of Anatomy}
\input{sections/2_related_work/subsections/visualization.tex}

\subsection{\label{sec::Video}Use of Video in Virtual Reality}
\input{sections/2_related_work/subsections/video_content.tex}

\subsection{\label{sec::Interactions}Interactions}
\input{sections/2_related_work/subsections/interactions.tex}

\subsection{\label{sec::Immersion}Immersion}
\input{sections/2_related_work/subsections/immersion.tex}

\subsection{\label{sec::MultiUser}Multi User}
\input{sections/2_related_work/subsections/multi_user.tex}

\subsection{\label{sec::TissueSimulation}Tissue Simulation}
\input{sections/2_related_work/subsections/tissue_simmulation.tex}

\subsection{\label{sec::SurgicalSimulations}Developed Software}
\input{sections/2_related_work/surgical_simulations/main.tex}

\subsection{\label{sec::RelatedWorkDiscussion}Discussion - Pros and Cons}
\input{sections/2_related_work/subsections/discussion.tex}